An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2012-03-30 Paper.tex
Moved project code to Noweb

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round]{natbib}
\usepackage[margin=1.25in]{geometry}
\usepackage[small]{caption}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\onehalfspacing

@@

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \texttt{gcalhoun@iastate.edu}.  Web:
    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  This paper
    has benefited from my conversations with Helle Bunzel, Graham
    Elliott, Yu-Chin Hsu, Pablo Pincheira, and Allan Timmermann; thank
    you.  I'd also like to thank Amit Goyal for providing computer
    code and data for his 2008 \textsc{rfs} paper with Ivo Welch
    \citep{GoW:08}.} \\ Iowa State University}

@@

\begin{abstract} 
  \noindent This paper proposes a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
  alternative model is still estimated with a fixed-length rolling
  window, but the benchmark is estimated with a recursive window. The
  resulting statistic is asymptotically normal even when the models
  are nested.  Moreover, the alternative model can be estimated using
  common model selection methods, such as the \aic\ or \bic.  This
  paper also presents a method to compare multiple models
  simultaneously while controlling family-wise error, and
  substantially improves existing block bootstrap methods for
  out-of-sample statistics.  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.

@@

\newpage \noindent This paper proposes an out-of-sample (\oos) test
statistic that is asymptotically normal with mean zero even when the
models studied are nested, proves that common block bootstrap methods
consistently estimate the statistic's distribution, and shows how the
statistic can be used to study many models simultaneously while
maintaining strong control of the familywise error (\fwe),
i.e. ensuring that the probability that the hypothesis that the model
has equal predictive ability to a benchmark is incorrectly rejected
for any of the models is no higher than a prespecified level.  \oos\
tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance \citep[see, for
example,][]{MeR:83,StW:03,GoW:08} and there is a substantial
literature developing the theoretical properties of these statistics,
beginning with \citet{DiM:95} and \citet{Wes:96} and continuing with
\citet{WeM:98}, \citet{Mcc:98,Mcc:00},
\citet{ClM:01,ClM:05-2,ClM:05,ClM:09b,ClM:11b,ClM:11}, \citet{CCS:01},
\citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00}, \citet{InK:04,InK:06},
\citet{Han:05}, \citet{Ros:05}, \citet{ClW:06,ClW:07}, \citet{Ana:07},
\citet{GiR:09,GiR:10}, \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11},
\cite{Pin:11}, \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among
others.\footnote{For recent reviews of this literature and additional
  references, see \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06},
  \citet{ClM:11c}, \citet{CoD:11}, and \citet{Gia:11}}

In a pair of papers, \citet{ClW:06,ClW:07} develop an \oos\ test of the
null hypothesis that a small benchmark model is correctly specified.
Their test compares the forecasting performance of a pair of nested
models, and the null hypothesis is that the innovations in the smaller
model form a martingale difference sequence.  This test procedure is
popular,\footnote{As of 12 September, 2011, \citet{ClW:06} has been
  cited by 28 papers indexed by the \textsc{isi} Web of Knowledge, and
  \citet{ClW:07} by 41. They have been cited by 132 and 172 papers
  indexed by Google Scholar respectively.} and one assumes that this
is due in part to the statistic's convenience.  The statistic is
approximately normal after adjusting for the estimation error of the
larger model.  Normality comes from a fixed-length rolling window, as
in \citet{GiW:06}, and the adjustment centers the statistic
appropriately.  This statistic is especially convenient because other
\oos\ tests for similar hypotheses \citep[among
others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a nonstandard
limit distribution and place restrictions on the models under
consideration, while other asymptotically normal statistics test a
different null hypothesis \citep{GiW:06} or place assumptions on the
models and \dgp\ that are often violated in empirical work
\citep{Wes:96,WeM:98,Mcc:00,DiM:95}.\footnote{\citet{DiM:95} assume
  that the models are not estimated. \citet{Wes:96,WeM:98,Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.}

@@

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,\footnote{Exceptions are \citepos{StW:07}
  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a likelihood ratio
test instead of an \textsc{lm} or Wald test.

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I'll present the
single-comparison statistic first and then the extension to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; further, let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the detailed assumptions required).  In
addition, let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the
pseudo-true coefficient of the regression of $y_{t+1}$ on $x_t$ and
define $\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear model
is correctly specified, so $\varepsilon_{t+1}$ is a martingale
difference sequence with respect to $\mathcal{F}_t = \sigma(y_{t+1},
x_t, v_t, y_t, x_{t-1}, v_{t-1}, \dots)$ then we can see immediately
that
\begin{equation}
  \label{eq:4}
  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
  - v_t) 
\end{equation}
with $R$ an arbitrary starting value\footnote{You will see momentarily
  why the summation begins at $R+1$ instead of 1.} and $P = T - R$,
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
  - v_t) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
  x_t\beta_0)^2 + (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big]
\end{equation}
almost surely.

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
    x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
    $\hat{\beta}_t$ given by Equation~\eqref{eq:8}.  Also define
    $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1} x_{t-1}'\big)^{-1}
    \sum_{t=2}^T \E x_{t-1} y_t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that includes
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2)}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
    \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
    long run variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma(y_t, z_{t-1}, y_{t-1}, z_{t-2},\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) = \Big\{\tfrac{2}{P}\sum_{t=R}^T x_t (2 x_t'\beta -
    y_{t+1} - \hat{y}_{1,t+1}) \Big\} \big(\tfrac1T \X'\X \big)^{-1}
    x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

@@

Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
clear that testing each hypothesis individually will often have a
probability greater than the tests' nominal size of rejecting at least
once.\footnote{Unless the statistics used for each test are completely
  interdependent, the probability will be strictly greater than the
  nominal size.}  Econometricians, e.g. \citet{Whi:00},
\citet{Han:05}, and \citet{ClM:11}, have emphasized statistics that
test families of hypotheses that control the probability any
hypothesis is rejected given that they all are true, known as
\textit{weak control of family-wise error} (\wfwe).  This paper
focuses instead on controlling the probability that at least one true
hypothesis is rejected given any combination of true and false
hypotheses, known as \textit{strong control of family-wise error}
(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
even though these papers only prove \wfwe, statistics based on
nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
and those based on the parametric bootstrap \citep{ClM:11} essentially
control \sfwe\ if the individual null hypotheses are strengthened
slightly as below (see Part~\ref{it:1} of Theorem~\ref{res:2} as well as
Remark~\ref{rem:2}).

@@

  Let the $*$-superscript denote a random variable with the
  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
  consider the following procedure:
  \begin{enumerate}
  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
    \{i : \tfrac1{\hat\sigma_i} |\bar{f}_{i}| > \hat{d}_j\}$, where
    $\hat{d}_j$ is the $1-2 \alpha$ quantile of $\max_{i \notin
      M_{j-1}} \tfrac{1}{\hat{\sigma}_i^{*}}|\bar{f}_{i}^{*} -
    \bar{f_i}(\hat{\beta}_{T+1})|$.
  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$
    and $\bar f_i > 0$.
  \end{enumerate}
  The following conclusions hold:
  \begin{enumerate}[i.]
  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
    procedure outlined above, but using the moving block bootstrap
    with block length 1, has probability at most $\alpha$ of rejecting
    one or more models in $I$.
  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is an \mds\ with respect to $\mathcal{F}_{lt}$
    against the one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If
    $p \to 0$ and $P p \to \infty$ as $T \to \infty$ (for the
    stationary bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$
    (for the moving or circular block bootstraps) then the procedure
    outlined above controls \sfwe\ at level $\alpha$ for the family of
    null hypotheses $H_1,\dots,H_m$.
  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
    and $P p \to \infty$ as $T \to \infty$ (for the stationary
    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
    moving or circular block bootstraps) then the procedure outlined
    above controls \sfwe\ at level $\alpha$ for the family of null
    hypotheses $H_1,\dots,H_m$.
  \end{enumerate}
\end{thm}

@@

\section{Monte Carlo Results}\label{sec:2}
\input{mc}
\section{Empirical Illustration}\label{sec:3}
\input{empirics}
\section{Conclusion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window---as do Clark and West---but estimating
the benchmark model with a recursive window.  Simulations indicate
that the new statistic behaves similarly to Clark and West's original
test, suggesting that the new statistic is a suitable replacement in
applied research.  The paper also presents a method for comparing the
benchmark model to several alternative models simultaneously and
improves block bootstrap procedures of \oos\ statistics.

>>>>

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,eco}
\usepackage[T1]{fontenc}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round]{natbib}
\usepackage[margin=1.25in]{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/simulationdefinitions}
\input{tex/empiricalresults}

@@

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \texttt{gcalhoun@iastate.edu}.  Web:
    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, and
    participants at the 2011 Midwest Econometrics Group meeting for
    helpful comments.  I'd also like to thank Amit Goyal for providing
    computer code and data for his 2008 \textsc{rfs} paper with Ivo
    Welch \citep{GoW:08}.} \\
  Iowa State University}

@@

\begin{abstract} 
  \noindent This paper proposes a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test.  The
  alternative model is still estimated with a fixed-length rolling
  window, but the benchmark is estimated with a recursive window. The
  resulting statistic is asymptotically normal even when the models
  are nested.  Moreover, the alternative model can be estimated using
  common model selection methods, such as the \aic\ or \bic.  This
  paper also presents a method to compare multiple models
  simultaneously while controlling familywise error, and
  substantially improves existing block bootstrap methods for
  out-of-sample statistics.  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset.

@@

\newpage \noindent This paper proposes an out-of-sample (\oos) test
statistic that is asymptotically normal with mean zero even when the
models studied are nested, proves that common block bootstrap methods
consistently estimate the statistic's distribution, and shows how the
statistic can be used to study many models simultaneously while
maintaining strong control of the familywise error (\fwe),
i.e. ensuring that the probability that the hypothesis that the model
has equal predictive ability to a benchmark is incorrectly rejected
for any of the models is no higher than a prespecified level.  \oos\
tests are commonly used in International Macroeconomics,
Macroeconomics, and Finance \citep[see, for
example,][]{MeR:83,StW:03,GoW:08} and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.\footnote{Other papers in this literature include
  \citet{WeM:98}, \citet{Mcc:98,Mcc:00},
  \citet{ClM:01,ClM:05-2,ClM:05,ClM:09b,ClM:11b,ClM:11},
  \citet{CCS:01}, \citet{CoS:02,CoS:04,CoS:07}, \citet{Whi:00},
  \citet{InK:04,InK:06}, \citet{Han:05}, \citet{Ros:05},
  \citet{ClW:06,ClW:07}, \citet{Ana:07}, \citet{GiR:09,GiR:10},
  \citet{HuW:10}, \citet{HLN:11}, \cite{InR:11}, \cite{Pin:11},
  \cite{RoS:11,RoS:11b}, and \citet{Cal:11}, among others.  For recent
  reviews of this literature and additional references, see
  \citet{McW:02}, \citet{CoS:06}, \citet{Wes:06}, \citet{ClM:11c},
  \citet{CoD:11}, and \citet{Gia:11}}

In a pair of papers, \citet{ClW:06,ClW:07} develop an \oos\ test of
the null hypothesis that a small benchmark model is correctly
specified.  Their test compares the forecasting performance of a pair
of nested models, and the null hypothesis is that the innovations in
the smaller model form a martingale difference sequence.  This test
procedure is popular, and one assumes that this is due in part to the
statistic's convenience.  The statistic is approximately normal after
adjusting for the estimation error of the larger model.  Normality
comes from a fixed-length rolling window, as in \citet{GiW:06}, and
the adjustment centers the statistic appropriately.  This statistic is
especially convenient because other \oos\ tests for similar hypotheses
\citep[among others]{Mcc:07,ClM:05,ClM:01,CoS:04,CoS:02,CCS:01} have a
nonstandard limit distribution and place restrictions on the models
under consideration, while other asymptotically normal statistics test
a different null hypothesis \citep{GiW:06} or place assumptions on the
models and \dgp\ that are often violated in empirical work
\citep{Wes:96,WeM:98,Mcc:00,DiM:95}.\footnote{\citet{DiM:95} assume
  that the models are not estimated. \citet{Wes:96,WeM:98,Mcc:00}
  implicitly assume that the models do not converge to the same limit,
  which rules out nesting.}

@@

Mixing window strategies is uncommon but needn't be. In most
applications, the null hypothesis imposes stability as well as equal
accuracy between the two models.  The benchmark model rarely allows
for breaks, parameter drift, or other forms of
instability,\footnote{Exceptions are \citepos{StW:07}
  \textsc{ima}(1,1) and \textsc{uc-sv} models of inflation.} but the
researcher is typically concerned about instability.  Indeed, concern
about instability is often given as a reason for doing an \oos\
analysis, especially with a short rolling window.\footnote{This
  motivation is discussed by \citet{StW:03}, \citet{PeT:05,PeT:07},
  \cite{GiW:06}, \citet{GoW:08}, \citet{ClM:09c}, and
  \cite{GiR:09,GiR:10}, among others.} A researcher could impose
stability on both models by using a recursive window or relax
stability for both by using a rolling window; either approach should
not affect the test's size, but may affect power.  But the researcher
could instead impose stability on the benchmark and relax it for the
alternative by using a recursive window for the benchmark and a
rolling window for the alternative model.  This approach could have a
power advantage and is similar in spirit to using a likelihood ratio
test instead of an \textsc{lm} or Wald test, which depend on just the
restricted or unrestricted model respectively.  Simulations presented
in Section~\ref{sec:2} show that mixing window strategies gives a
substantial power advantage when there are breaks.

@@

\section{Out-of-Sample Model Comparisons}\label{sec:1}
This section presents the new \oos\ statistic.  I'll present the
single-comparison statistic first and then the extension to multiple
comparisons.  Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; further, let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the detailed assumptions required).  In
addition, let $\beta_0 = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the
pseudo-true coefficient of the regression of $y_{t+1}$ on $x_t$ and
define $\varepsilon_{t+1} = y_{t+1} - x_t'\beta_0$.  If the linear
model is correctly specified, so $\varepsilon_{t+1}$ is a martingale
difference sequence with respect to $\mathcal{F}_t = \sigma((x_t, v_t,
y_t), (x_{t-1}, v_{t-1}, y_{t-1}),\dots)$ then we can see immediately that
\begin{equation}
  \label{eq:4}
  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
  - v_t) 
\end{equation}
with $R$ an arbitrary starting value\footnote{You will see momentarily
  why the summation begins at $R+1$ instead of $1$.} and $P = T - R$,
obeys an \mds\ \clt\ (assuming that its variance is uniformly
positive) and is asymptotically normal as $P \to \infty$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \varepsilon_{t+1} (x_t'\beta_0
  - v_t) = \tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T \Big[(y_{t+1} -
  x_t\beta_0)^2 + (y_{t+1} - v_t)^2 + (x_t'\beta_0 - v_t)^2 \Big].
\end{equation}

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window: $\hat{y}_{0,t+1} =
    x_t'\hat{\beta}_t$ for some vector of predictors $x_t$ with
    $\hat{\beta}_t$ given by Equation~\eqref{eq:8}.  Also define
    $\beta_0 = \big(\sum_{t=2}^{T} \E x_{t-1} x_{t-1}'\big)^{-1}
    \sum_{t=2}^T \E x_{t-1} y_t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that includes
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f =
    \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$. The
    processes $f_t(\beta_0)$ and $x_t(y_{t+1} - x_t'\beta_0)$ are
    covariance stationary and $\bar f(\beta_0)$ has uniformly positive
    long run variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) = \Big\{\tfrac{2}{P}\sum_{t=R}^T x_t (2 x_t'\beta -
    y_{t+1} - \hat{y}_{1,t+1}) \Big\} \big(\tfrac1T \X'\X \big)^{-1}
    x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

\begin{rem}
  \citet{GiW:06} and \citet{ClW:06,ClW:07} emphasize the rolling
  window but claim that their results hold for a fixed-length fixed
  window as well, where the unknown coefficients are estimated only
  once using the first $R$ observations.  This claim is true but not
  obviously so.  The proof for the rolling window is based on the idea
  that the forecast errors are weakly dependent because they are a
  function of a finite number of consecutive weakly dependent
  observations.  But using a fixed window introduces another source of
  dependence.  All of the forecasts depend on the same coefficient
  estimates.  One can prove that their results apply to fixed window
  forecasts by using a coupling argument similar to \citepos{Cal:11}.
  Interested readers should refer to \citet{Cal:11} for the argument
  and to \citet{MeP:02} for a review of the necessary coupling
  results.
\end{rem}

@@

Suppose we have the family of hypotheses, $H_1,\dots,H_J$.  It is
clear that testing each hypothesis individually will often have a
probability greater than the tests' nominal size of rejecting at least
once.\footnote{Unless the statistics used for each test are completely
  interdependent, the probability will be strictly greater than the
  nominal size.}  Econometricians, e.g. \citet{Whi:00},
\citet{Han:05}, \cite{HuW:10}, and \citet{ClM:11}, have emphasized
statistics that test families of hypotheses that control the
probability any hypothesis is rejected given that they all are true,
known as \textit{weak control of familywise error}
(\wfwe).\footnote{An exception is \citet{HHK:10} who combine
  \citepos{RoW:05} StepM with \citepos{Han:05} threshold rule to
  control \sfwe\ for certain families of one-sided tests.}  This paper
focuses instead on controlling the probability that at least one true
hypothesis is rejected given any combination of true and false
hypotheses, known as \textit{strong control of familywise error}
(\sfwe).  For most empirical work, \sfwe\ is desired; fortunately,
even though these papers only prove \wfwe, statistics based on
nonparametric block bootstraps \citep{Whi:00,Han:05} can be shown to
control \sfwe\ as well \citep[this follows directly from][]{RoW:05}
and those based on the parametric bootstrap \citep{ClM:11} essentially
control \sfwe\ if the individual null hypotheses are strengthened
slightly as below (see Part~(\ref{it:1}) of Theorem~\ref{res:2} as
well as Remark~\ref{rem:2}).  \citet{HuW:10} propose that researchers
construct critical values from the asymptotic joint distribution of
the test statistics and can control \sfwe\ as long as there is a
consistent estimate of that distribution.

@@

  Let the $*$-superscript denote a random variable with the
  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
  consider the following procedure:
  \begin{enumerate}
  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
    \{i : \tfrac1{\hat\sigma_i} |\bar{f}_{i}| > \hat{d}_j\}$, where
    $\hat{d}_j$ is the $1-2 \alpha$ quantile of $\max_{i \notin
      M_{j-1}} \tfrac{1}{\hat{\sigma}_i^{*}}|\bar{f}_{i}^{*} -
    \bar{f_i}(\hat{\beta}_{T+1})|$.
  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$
    and $\bar f_i > 0$.
  \end{enumerate}
  The following conclusions hold:
  \begin{enumerate}[i.]
  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
    procedure outlined above, but using the moving block bootstrap
    with block length $1$, has probability at most $\alpha$ of rejecting
    one or more models in $I$.
  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is an \mds\ with respect to $\mathcal{F}_{lt}$
    against the one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If
    $p \to 0$ and $P p \to \infty$ as $T \to \infty$ (for the
    stationary bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$
    (for the moving or circular block bootstraps) then the procedure
    outlined above controls \sfwe\ at level $\alpha$ for the family of
    null hypotheses $H_1,\dots,H_m$.
  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
    and $P p \to \infty$ as $T \to \infty$ (for the stationary
    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
    moving or circular block bootstraps) then the procedure outlined
    above controls \sfwe\ at level $\alpha$ for the family of null
    hypotheses $H_1,\dots,H_m$.
  \end{enumerate}
\end{thm}

@@

\section{Monte Carlo Results}\label{sec:2}
I'll conduct two brief Monte Carlo experiments to demonstrate that the
modified version of \citepos{ClW:07} statistic performs similarly to
their original test in the situations they study.\footnote{All of
  these simulations were programmed in R \citep{R:2-13-0} and use the
  \textsc{MASS} \citep{VeR:02}, xtable \citep{Dah:09}, and dbframe
  \citep{Cal:10b} packages.  Version
  information is listed in the bibliography.}  I'll use both of the
\dgp s they consider as well as a modification to study the
performance of the statistics if there is instability.
